Total Score

### 2023-02-03 src/MSAtotal_scores.Rmd
working on barplot

score_tidy <- criteria_all %>% 
  pivot_longer(cols = c(real_estate_score, landlord_score, financial_score:climate_risk),
               names_to = "criteria",
               values_to = "criteria_score") %>% 
  filter(city_msa != "Portland") %>% 
  group_by(city_msa)

ggplot(data = score_tidy, aes(y = city_msa, x = total_score_owen, fill = criteria)) + 
    geom_col()

>>>>

score_tidy <- criteria_all %>% 
  pivot_longer(cols = c(4:18),
               names_to = "criteria",
               values_to = "criteria_score") %>% 
  filter(city_msa != "Portland") %>% 
  group_by(city_msa) %>% 
  filter(criteria %in% c("real_estate_score", "landlord_score", "financial_score", "climate_impact", "electricity", "climate_risk", "climate_EAL_risk", "health_impact", "electricity"))

ggplot(data = score_tidy, aes(y = city_msa, x = criteria_score, fill = criteria)) + 
    geom_col()
